Scheeper's Meager-NWD Game and the Menger Game

### 2014-11-27 phd/dissertation/chapter5.tex
define cantor tree of L spaces

\begin{proof}
  Let $\sigma$ be a predetermined strategy for $\pl K$, and define the
  counterattack $H:\omega\to\mc K(X)$ by
  $H(n)=(n\cup\sigma(n+1))\setminus\sigma(n)$. Then for any neighborhood
  $U_S$ of $\mc F$, $S$ is infinite, and since
  $\bigcup_{n<\omega} H(n)\supseteq\omega\setminus\sigma(0)$, $U_S$ meets
  infinitely many of the finite $H(n)$. Thus $\sigma$ is not a winning
  predetermined strategy.
\end{proof}

@@

  Consider the set of all legal attacks $A\subseteq\omega^\omega$ by
  $\pl P$ against $\sigma$. For $n<\omega$, note that for any $f\in A$,
  $f$ maps only $n$ points into $n^2$, so the range of $f$ is coinfinite.
  Then $\mc I=\{\ran f : f\in A\}$ is an ideal, and if
  $\mc F\supseteq\{\omega\setminus I: I\in\mc I\}$, then $\sigma$ is a
  winning predetermined strategy.
\end{proof}

% \begin{prop}
%   If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
%   then $K \not\prewin \gruKPGame{X}$
%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
% \end{prop}

% \begin{thm}
%   Then there is an ultrafilter $\mathcal{F}$ such that
%   then $K \prewin \gruKPGame{X}$ and $K \tactwin \gruKPGame{X}$
%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
% \end{thm}

% \begin{thm}
%   Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
%   Then $P \win \gruKPGame{M}$.
% \end{thm}

% \begin{thm}
%   Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
%   Then $K \prewin \gruKPGame{S}$ and $K\tactwin \gruKPGame{S}$.
% \end{thm}

% (TODO: Maybe consider claim
% $K \prewin \gruKPGame{X}$ $\Rightarrow$ $X$ is a $k$-space)

>>>>

\begin{proof}
  Let $\sigma$ be a predetermined strategy for $\pl K$, and define the legal
  counter-attack $H:\omega\to\mc K(X)$ by
  $H(n)=(n\cup\sigma(n+1))\setminus\sigma(n)$. Then for any neighborhood
  $U_S$ of $\mc F$, $S$ is infinite, and since
  $\bigcup_{n<\omega} H(n)\supseteq\omega\setminus\sigma(0)$, $U_S$ meets
  infinitely many of the finite $H(n)$. Thus $\sigma$ is not a winning
  predetermined strategy.
\end{proof}

@@

  Consider the set of all legal attacks $A\subseteq\omega^\omega$ by
  $\pl P$ against $\sigma$. For $\{f_i:i\leq m\}\in [A]^{<\omega}$ and
  $m<n<\omega$, each $f_i$ maps only $n$ points into $n^2$, so
  $\bigcup_{i\leq m}\ran{f_i}$ is coinfinite.
  Then $\mc G'=\{\omega\setminus\ran f : f\in A\}$ is contained in a free
  ultrafilter $\mc G$, and if $\mc F=\mc G$, then $\sigma$ is a
  winning predetermined strategy.
\end{proof}

It is not possible to prove that $\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$
for arbitrary free ultrafilters in $ZFC$.

\begin{defn}
  A \term{selective ultrafilter} $\mc F$ is a free ultrafilter with the
  property that for every
  partition $\{B_n : n < \omega\}$ of nonempty subsets of $\omega$ such that
  $B_n \not\in \mathcal{F}$ for all $n$, there exists $A \in \mc{F}$ such
  that $|A \cap B_n|=1$ for all $n$.
\end{defn}

\begin{thm}
  CH implies the existence of a selective ultrafilter.
  \cite{MR0080902}
\end{thm}

\begin{thm}
  If $\mc F$ is a selective ultrafilter, then
  $\pl K\not\prewin \gruKPGame{\omega\cup\{\mc F\}}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a predetermined strategy for $\pl K$ such that
  $\sigma(n)\supset\bigcup_{m<n}\sigma(m)$.
  Then define $B_n=\omega\cap(\sigma(n+1)\setminus\sigma(n))$. Since $B_n$
  is always nonempty finite, $B_n\not\in\mc F$ and there exists $A\in \mc F$
  such that $|A\cap B_n|=1$.

  Define the legal counter-attack $p:\omega\to\omega\cup\{\mc F\}$ by
  $p(n)\in A\cap B_n=A\cap(\sigma(n+1)\setminus\sigma(n))$. Since
  $A=(A\cap\sigma(0))\cup\{p(n):n<\omega\}$, $\{p(n):n<\omega\}\in\mc F$.
  Therefore, every neighborhood of $\mc F$ intersects infinitely many of
  the $p(n)$, and $p$ defeats the predetermined strategy $\sigma$.
\end{proof}

Of particular note is that the author knows of no examples of a
non-$k$-space such that $K\prewin\gruKPGame{X}$.

\begin{ques}
  Does $K\prewin\gruKPGame{X}$ imply $X$ is a $k$-space?
\end{ques}

\section{$k+1$-tactics and marks for $\gruKPGame{X}$}

While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
strategies, this result cannot be
immediately extended to $\gruKPGame{X}$. However, this section will
demonstrate a non-trivial example of a space $\mb X$ for which
$\pl K\win\gruKPGame{\mb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\mb X}$
for any $k<\omega$.

\begin{defn}
  An $L$-space is a herditarally Lindel\"of, non-separable space.
\end{defn}

\begin{thm}
  Under $CH$(?), there exists a zero-dimensional, compact $L$-space.
  Furthermore, there exists a point-countable collection of clopen sets
  $\mc U=\{U_\alpha:\alpha<\omega_1\}$ in $X$ such
  that every point-finite subcollection of $\mc U$ is countable.
\end{thm}

\begin{proof}
  (TODO or find citation)
\end{proof}

\begin{defn}
  Let $\mb X=(X\times 2^{<\omega})\cup 2^\omega$ denote a Cantor tree
  of zero-dimensional, compact $L$-spaces $X$ with a point-countable collection
  of clopen sets $\mc U=\{U_\alpha:\alpha<\omega_1\}$ such
  that every point-finite subcollection of $\mc U$ is countable.
  The topology on $\mb X$ is
  given by decaring $U\times\{s\}$ to be an open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be an open
  neighborhood of $f\in 2^\omega$ for each $\alpha<\omega_1$ and $m<\omega$.
\end{defn}
